### 2016-03-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Updated hose stream report, plotting script & FDS exp report

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
% [FDS intro] 
Fire dynamics 
% [importance of validation]

% [this report is (1/2) --> experimental setup and procedure]
This report describes the full-scale fire test experiments that are used for the FDS model validation of [...]. Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings. During each test, propane was provided to three burners at a known flow rate [to create a diff flame]. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected.

>>>>

% ================
% = Introduction =
% ================
\chapter{Introduction}
\label{chap:Introduction}
% [FDS intro]

% [importance of validation]

% [this report is (1/2) --> experimental setup and procedure]
This report describes a series of full-scale fire test experiments that were conducted for the purpose of FDS model validation. Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings. During each test, propane was provided to three diffusion flame burners at a measured flow rate. Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structures while ventilation patterns were changed by opening and closing specific doors and roof vents.

### 2016-03-03 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream report, plotting script & FDS exp report

NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{}. The studies have resulted in guidance to the fire service regarding ventilation tactics. However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams is also needed.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 13 for three hose stream patterns.}
	\label{fig:Test_33_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
	\label{fig:Test_34_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

>>>>

One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics. NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{}. The studies have resulted in guidance to the fire service regarding ventilation tactics. However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams is also needed.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
	\caption{Average velocity through the interior doorway during Test 33 for three hose stream patterns.}
	\label{fig:Test_33_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
	\caption{Average velocity through stairwell door during Test 34 for three hose stream patterns.}
	\label{fig:Test_34_BDP_A6_Avg_All}
\end{figure}
\FloatBarrier
